---
title: "Mini Data-Analysis Deliverable 1"
author: "Yihang Chen"
output: github_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1. Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

```
install.packages("devtools")
devtools::install_github("UBC-MDS/datateachr")
```

2. Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
```

3. Make a repository in the https://github.com/stat545ubc-2021 Organization. You will be working with this repository for the entire data analysis project. You can either make it public, or make it private and add the TA's and Vincenzo as collaborators. 

4. When you go to submit, submit a URL to your repository to canvas. 

# Instructions

More details regarding the instructions and points allocated to each task can be found below. Briefly,

+ Each milestone is worth 30 points. The number of points allocated to each task will be annotated within each deliverable. Tasks that are more challenging will often be allocated more points.

+ 10 points will be allocated to the reproducibility, cleanliness, and coherence of the analysis. While the three milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as 3 chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

# Learning Objectives

By the end of this milestone, you should:

+ Become familiar with your dataset of choosing
+ Think of 4 questions that you would like to answer with your data
+ Generate a reproducible and clear report using R Markdown

# Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

+ *apt_buildings*: Acquired courtesy of The City of Toronto’s Open Data Portal. It currently has 3455 rows and 37 columns.

+ *building_permits*: Acquired courtesy of The City of Vancouver’s Open Data Portal. It currently has 20680 rows and 14 columns.

+ *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

+ *flow_sample*: Acquired courtesy of The Government of Canada’s Historical Hydrometric Database. It currently has 218 rows and 7 columns.

+ *parking_meters*: Acquired courtesy of The City of Vancouver’s Open Data Portal. It currently has 10032 rows and 22 columns.

+ *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

+ *vancouver_trees*: Acquired courtesy of The City of Vancouver’s Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

+ We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

+ Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

_My choice: 1: cancer_sample; 2: flow_sample; 3: parking_meters; 4: steam_games_   

1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*. 

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

1. Explore the selected dataset1: cancer_sample.
```{r}
class(cancer_sample)
names(cancer_sample)
ncol(cancer_sample)
nrow(cancer_sample)
length(cancer_sample)
summary(cancer_sample)
glimpse(cancer_sample)
```

2. Explore the selected dataset2: flow_sample.
```{r}
class(flow_sample)
names(flow_sample)
ncol(flow_sample)
nrow(flow_sample)
length(flow_sample)
summary(flow_sample)
glimpse(flow_sample)
```

3. Explore the selected dataset3: parking_meters.
```{r}
class(parking_meters)
names(parking_meters)
ncol(parking_meters)
nrow(parking_meters)
length(parking_meters)
summary(parking_meters)
glimpse(parking_meters)
```
4.Explore the selected dataset4: steam_games.
```{r}
class(steam_games)
names(steam_games)
ncol(steam_games)
nrow(steam_games)
length(steam_games)
summary(steam_games)
glimpse(steam_games)
```

1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation. 

_I would choose dataset 1: cancer_sample and dataset 4:steam_games because both of them contains relatively fewer numbers of columns and rows (compared with all the others). Apart from that, when looking at their summaries and variables, those two are the ones make the most sense to me._

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!


_For the data set 1 (cancer_sample), I am interested to study how the diagnosis is related to other variables, such as texture_mean and area_mean._

_For the dadaset4(steam_games), I am interested to study how the original price is related to other variables, such as types, discount price and achievements._ 

_After comparing the above two options, I decide to follow up on the dataset4 (steam_games) and to study more on the original prices of the steam games._ 


# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. Remember, marks will be awarded for completion of the 4 tasks, but 10 points of the whole project are allocated to a reproducible and clean analysis. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.


# Task 2: Exploring your dataset (15 points)

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1. Plot the distribution of a numeric variable.
2. Create a new variable based on other variables in your data (only if it makes sense)
3. Investigate how many missing values there are per variable. Can you find a way to plot this?
4. Explore the relationship between 2 variables in a plot.
5. Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6. Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7. Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8. Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

# Task 3: Write your research questions (5 points)

So far, you have chosen a dataset and gotten familiar with it through exploring the data. Now it's time to figure out 4 research questions that you would like to answer with your data! Write the 4 questions and any additional comments at the end of this deliverable. These questions are not necessarily set in stone - TAs will review them and give you feedback; therefore, you may choose to pursue them as they are for the rest of the project, or make modifications!

<!--- *****START HERE***** --->

##Answers to Questions 2.1 

1. Exercise#1: Plot the distribution of a numeric variable.

_For the first exercise, I want to plot the histogram of the orginal prices of the steam games. In order to explore the data for orginal prices, I arranged the dataset in decreasing order for original price. I found two games with abnormal prices (extremely high), which are 730640.00 and 650560.00. All the others have an original price below 1000. Therefore, I filtered the dataset with original price lower than 1000 and then plot it with geom_histogram function.I set the binwidth to 5 so it is easier to observe the difference and the peaks._ 

```{r This is the histogram plot for original price of steam games}
original_price_histogram <- steam_games %>%
  filter(original_price < 1000) %>%
  ggplot(aes(original_price)) +
  geom_histogram(binwidth = 5)

print(original_price_histogram)
```

_The first research question I want to study here is how the original prices of steam games are distributed. From the histogram, I observe that the prices of the most games lie within the range between 0 to 250. Only a few games are more than 250 dollars. This suggested that a game with lower price is more common or acceptable to the public._


2. Exercise#2: Create a new variable based on other variables in your data (only if it makes sense)

_For the second exercise, I want to create a new variable which is the difference of the price between original price and discount price. For this exercise, I am curious about how much is game usually discounted during a promotion._ 

_Therefore, I created a new variable using original_price minus discount_price, and put them in a new table. I tried to drop the NA values but decided not to eventually because I think it is important to leave those with no discount price there. Therefore people can have a sense about how many games are discounted while how many games are not discounted in the same time._

```{r This shows a table with the original price, discount price and price different for all the games provided.}
table_with_price_difference <- steam_games %>%
  mutate(price_difference = original_price - discount_price) %>%
  select(id, original_price,discount_price,price_difference)

table_with_price_difference
```

_The second research question I want to discover here is how much is a game usually discounted during a promotion. Therefore, I created a new variable which is the price difference. Interestingly, I observe that it is not all the case that discount price is lower than the original price. Some games have a discount price higher than the original price, which gives a negative price_difference. This is very surprising to me._


3. Exercise#4: Explore the relationship between 2 variables in a plot.)

_For the third exercise, I want to explore the relationship between original price and achievement. Therefore, I created a point plot with original price on the x- axis and achievement on the y-axis. I filter with original price lower than 1000 because there are two games with extremely high prices which I think is abnormal. I also drop the NA ones to show a more organized plot. I set the opacity to 0.3. Therefore if a position has a darker color, it means there are more repeated points at that position._

```{r This shows a point plot with original price and achievements}
price_vs_achievement_plot <- steam_games %>%
   filter(original_price <1000) %>%
   select(original_price, achievements) %>%
   drop_na() %>% 
   ggplot(aes(original_price, achievements))+
   geom_point(alpha=0.3)

print(price_vs_achievement_plot)

```
_The third research question I want to study here is if games with higher original price will always have a higher score for the achievement. From the point plot that I have made here, it showed that there is no clear positive linear relationship between original price and achievement. Therefore, this suggests that games with higher original prices do not always have a higher score for achievements._

4. Exercise#6. Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!

_In the forth exercise, I am curious about the relationship between different types of games and their original prices. I filtered the original price with lower than 1000 to drop the abnormal prices, which is explained in previous exercises as well. Then I put types on the x-axis and original price on the y-axis and create a box plot. I use grey color to fill the box and set the transparency to 0.3 so the repeated points are easier to be observed._

```{r The boxplot of the types and origianl price of the steam games}

type_vs_price_boxplot <- steam_games %>%
  filter(original_price < 1000) %>%
  ggplot(aes(types,original_price)) +
  geom_boxplot(fill="grey", alpha = 0.3)

print(type_vs_price_boxplot)
```
_The forth research question I want to study from this exercise is if there is any difference of the original prices between different types of games. From the box plot I observe that most games are "app" games, and they have a lower mean and medium prices compared with "bundle" and "sub" games. However, the price range of "app" games is a lot wider than the others._ 

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching